---
title: "Instrumentos de Análisis Urbano I"
author: "Florencia Kihara, Santiago Soubie y Victoria Marco"
date: "15/5/2021"
output: html_document
---
```{r}
library(tidyverse)
library(sf)
library(leaflet)
```

```{r}
str()
```


calles <- read_sf("https://github.com/SSoubie/MEU-Hackers/blob/main/Datasets/callejero.geojson")

```{r}
properati2021 <- properati %>% 
  separate(created_on, c("ano", "mes", "dia"), sep = "-") %>% 
  filter(ano=="2021" & l2=="Capital Federal" & price!="NA") %>% 
  select(-start_date, -end_date, -mes, -dia, -l4, -l5, -l6)
```


```{r}
calles <- st_read("C:/Users/Santi/Desktop/Santi/Ciencia de Datos/Instrumento de Analisis Urbano/TP/Datasets/callejero.geojson")
```

```{r}
estaciones <- st_read("C:/Users/Santi/Desktop/Santi/Ciencia de Datos/Instrumento de Analisis Urbano/TP/Datasets/estacionsubte.geojson")
```

```{r}
properati <- read.csv("C:/Users/Santi/Desktop/Santi/Ciencia de Datos/Instrumento de Analisis Urbano/TP/Datasets/rent_properati_2020_2021.csv",
                      encoding = "UTF-8",
                      stringsAsFactors = TRUE)
```
